{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-02-02 thesis/landslide.tex
bit more

@@

However, it also offers several special-case features
which even some students have sometimes noticed as being more clever than Simics's stack tracer.
I document those features here.
If you prefer to read about these in code than in prose, see {\tt stack\_trace()} in {\tt stack.c}.

>>>>

The infrastructure for producing the diagnostic output to help users understand their bugs
can be classified in three parts:
the symbol table glue, the excessively clever stack tracer, and the preemption table generator.

@@

However, it also offers several special-case features
which even some students have sometimes noticed as being more clever than Simics's stack tracer.
I document those features here.
As a common point of implementation among them,
Landslide traces the stack pointer {\tt esp} in addition to the base pointer {\tt ebp};
not only updating it whenever dereferencing the base pointer,
but also when decoding simple assembly routines, finding ``hidden'' stack frames without base pointers,
identifying system call wrappers, and so on.
The corresponding code lives in {\tt stack\_trace()} in {\tt stack.c}.
